\textbf{Emergency Service Location Optimization in a Multi-Zone County based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
added code stuffs
add stuff about individual cases

\usepackage{url}
\usepackage{caption}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
\graphicspath{{./Pictures/}}

@@

\subsubsection{$n=3$}

\subsubsection{$n=2$}

\subsubsection{$n=1$}

@@

\section{Strengths and Weaknesses}

@@

\appendix
\section{Code}

>>>>

\usepackage{url}
\usepackage{caption}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
\usepackage{minted}
\usemintedstyle{colorful}
\graphicspath{{./Pictures/}}

@@

\subsubsection{$n=3$}
We ran the greedy algorithm for $n=3$ and we got that ambulances should be placed in zones
2, 3, and 5. This arrangement has ambulances cover all of zones 2-6 and half (25000/50000) of
zone 1.

\subsubsection{$n=2$}
We ran the greedy algorithm for $n=2$ and we got that ambulances should be placed in zones
2 and 5. This arrangement has ambulances cover all of zones 2, 4-6, half (25000/50000) of
zone 1, and none of zone 3.

\subsubsection{$n=1$}
We ran the greedy algorithm for $n=1$ and we got that our ambulance should be placed in zone 5. This arrangement allows the single ambulance to cover all of zone 4-6.

@@

\section{Strengths and Weaknesses}
Our program is readily scalable to larger cities and larger numbers of ambulances, and due to using an
efficient greedy heuristic it runs in polynomial time.

@@

\appendix
\section{Code}
\inputminted[fontsize=\footnotesize]{python}{../Code/optimizer.py}
